Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-12 sas2015/content/background.tex
minor changes

\subsection{IFDS}\label{sec:bgifds}
The IFDS framework~\cite{reps1995precise} is a precise and efficient algorithm for data-flow analysis
%. IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and
that has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
The IFDS framework is an instance of the \textit{functional approach} to data-flow analysis~\cite{pnueli1981two}
because it constructs summaries of the effects of called procedures.
The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
and whose data-flow functions are \textit{distributive}.
A function $f$ is distributive if 
$f(x_1\sqcap x_2)=f(x_1)\sqcap f(x_2)$.

@@

    To eliminate infeasible paths due to correlated calls, we encode the taint
    analysis using environments $\textsf{Env}(D,L)$, where $D$ is the set of
    variables and $L$ is a map from receiver variables to sets of possible
    types. The interpretation of such an environment $e$ is that a given variable
    $v \in D$ may contain a secret value in an execution in which the runtime
    types of the objects pointed to be the receiver variables are in the sets
    specified by $e(v)$.
\end{example}

>>>>

\subsection{IFDS}\label{sec:bgifds}
The IFDS framework~\cite{reps1995precise} is a precise and efficient algorithm for data-flow analysis
%. IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and
that has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
The IFDS framework is an instance of the \textit{functional approach} to data-flow analysis~\cite{pnueli1981two}
because it constructs summaries of the effects of called procedures.
The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain is a \textit{subset} of a \textit{finite} set $D$,
and whose data-flow functions are \textit{distributive}.
A function $f$ is distributive if 
$f(x_1\sqcap x_2)=f(x_1)\sqcap f(x_2)$.

@@

    To eliminate infeasible paths due to correlated calls, we encode the taint
    analysis using environments $\textsf{Env}(D,L)$, where $D$ is the set of
    variables and $L$ is a map from receiver variables to sets of possible
    types. The interpretation of such an environment $e$ is that a given variable
    $v \in D$ may contain a secret value in an execution in which the runtime
    types of the objects pointed to by the receiver variables are in the sets
    specified by $e(v)$.
\end{example}
